DisCon Adult Study 1 (Absolute and Relative Strength of Inputs)

### 2019-01-18 analysis/01_adult_speakerchange_preference.Rmd
analysis code and data for speaker change experiment

---
title: "DisCon Speaker Change Adult Analysis"
output: html_document
---

@@

files <- dir("../../adult_600_speakerchange/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_speakerchange/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

>>>>

---
title: "DisCon Speaker Change Adult with Preference Analysis"
output: html_document
---

@@

files <- dir("../../adult_600_speakerchange_preference/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_speakerchange_preference/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

### 2019-01-18 analysis/01_study1_adult.Rmd
data for different intros
analysis code and data for speaker change experiment

---
title: "DisCon Adult Study 1"
output: html_document
---

@@

write.csv(data_high, file="../data/01_study1_adult_low.data.csv")
data_low <- read_csv(file="../data/01_study1_adult_low.data.csv")

>>>>

---
title: "DisCon Adult Study 1 (Absolute and Relative Strength of Inputs)"
output: html_document
---

@@

write.csv(data_low, file="../data/01_study1_adult_low.data.csv")
data_low <- read_csv(file="../data/01_study1_adult_low.data.csv")
